\chapter{Design Science Research}
\label{chapter:DSR}

In this chapter, to answer the question ``Which projections can we create to help developers get appropriate feedback about rules?'', we undertook a design science research (DSR) approach.
In section \ref{section:dsr_method} we describe the method of this DSR.
Section \ref{section:dsr_results} examines the outcomes of our research.
Finally, in section \ref{section:dsr_discussion} we discuss the threats to validity of our approach.

\input{Sections/DSR/DSR_Method}

\input{Sections/DSR/DSR_Results}

\input{Sections/DSR/DSR_Discussion}

\section{Summary}
In this chapter, we presented a description of the details of the DSR that we conducted.
We pursued two languages.
In our pilot study we implemented the Really Simple Drools language, and a number of projections on top of this.
Once we had established the usefulness of this approach, we created the language Drools-Lite which was a language that would be recognisable to experienced Drools developers.

Of the projections we created, the most capable were the Spreadsheet-like and Decision table like projections.
These both succeeded in massively reducing the screen real estate required.
Other advantages included being able to group related rules and being able to visually scan which rules used the same facts and properties.

Rules with complex nested conditions could not be shown in the tabular projections, however this was mitigated by the ability to mix notations.
Rules too complicated for the tabular projections could be shown with textual projections in the same file.