\chapter{Questionaire Text}\label{Appendix:Questionaire_text}

Note: This questionnaire was presented on Survey Monkey and thus the text here is a best approximation of their paging system.


\section{Page 1 - Introduction}

Thank you for taking part in this research.

According to Survey Monkey, this survey should take 5 minutes to complete, when we tested it, the average was closer to 9 minutes.

It is part of a research master's project by Paul Spencer at the University of Amsterdam.

The purpose is to determine whether projectional editing can be used to aid the comprehensibility of business rules from the point of view of a software developer.

We are using Drools as our example business rules language.

You were selected as you asked or answered a Drools question on StackOverflow, listed Drools as a skill on your LinkedIn profile, or were referred to this survey by someone who did.

It is therefore assumed you are aware of what Drools is.

Projectional editing is a form of writing computer programs directly rather than writing text and having that parsed to create the program.
This allows multiple views and editors for the same code.

In this survey, we will present you with a few of these views.

On the following page, there is an animated GIF that will give a small demonstration of what this means.

\section{Page 2 - Example of Projectional editing in Drools}

Below is an example of a projectional implementation of Drools.

The top part is a tabular projection of the program.
The bottom part is a textual projection of the same program shown at the same time.

Here we are editing in the tabular projection. 
Because the textual projection is just another view on the same underlying program, it is updated at the same time.

\emph{Here is placed an animated Gif}

Question: What is your first reaction to this mode of code editing?
Options: Very positive, Somewhat positive, Neutral, Somewhat negative, Very negative

\section{Page 3 - Positive about projectional editing}
\emph{This page is only selected if the user chose very positive or somewhat positive}

Question: how would this coding style be useful to your interactions with Drools?
This is an open question with a text box.

\section{Page 4 - negative about projections}
\emph{This page is only selected if the user chose very positive or somewhat positive}
